\vfill World of Warcraft's New Way to Get You Hooked

### 2013-04-05 paper.tex
14. Better explaination of relation to Public Good

\paragraph{World Of Warcraft Teaches Players Life Skills\\}
In a three year study of over 30,000 MMORPG users, over 50\% of users said that they learned valuable leadership skills that have helped them outside of the game. \cite{MotivationsAndDerviedExperiences}
Many features in World of Warcraft drive the players to socialize. \footnote{Having over two months of play time in-game with the last play session less than a week ago, I consider myself qualified to discuss the mechanics of World of Warcraft without citation.} The best gear and most prestigious titles are only available to users who group together to take on challenges that cannot be conquered by oneself. These challenges require intense coordination and communication as well as skilled players. Without grouping together, players have no chance of getting these items or attaining these statuses.
Guilds offer perks to their members through mechanics built into the game. As guilds grow in size and their members complete quests and dungeons, these guilds level up and offer a variety of rewards. Becoming part of a community of people is rewarded in-game.

Friendships and powerful experiences help us grow as individuals. MMORPGs, like World of Warcraft, are providing their users with leadership skills, strong friendships, and powerful experiences.

>>>>

\paragraph{World Of Warcraft Teaches Players Life Skills\\}
In a three year study of over 30,000 MMORPG users, over 50\% of users said that they learned valuable leadership skills that have helped them outside of the game. \cite{MotivationsAndDerviedExperiences}
Many features in World of Warcraft drive the players to socialize. \footnote{Having over two months of play time in-game with the last play session less than a week ago, I consider myself qualified to discuss the mechanics of World of Warcraft without citation.} The best gear and most prestigious titles are only available to users who group together to take on challenges that cannot be conquered by oneself. These challenges require intense coordination and communication as well as skilled players. Without grouping together, players have no chance of getting these items or attaining these statuses.
Guilds offer perks to their members through mechanics built into the game. As guilds grow in size and their members complete quests and dungeons, these guilds level up and offer a variety of rewards. Becoming part of a community of people is rewarded in-game.
\newline
\newline
Friendships and powerful experiences help us grow as individuals. World of Warcraft is improving the public good by improving the individuals that play it in ways that promote social skills and leadership skills. These skills benefit not only the player but also the people the player interacts with outside of the game. MMORPGs, like World of Warcraft, are providing their users with leadership skills, strong friendships, and powerful experiences that they take with them to interactions outside the game.
